### 2014-05-26 ms/ms.Rmd
Add Ishihara as 3rd coauthor, details about contributions

We (D. Falster and R. Duursma, with the help of D Barneche, A Vårhammer and R FitzJohn) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$dataset))` different published and unpublished studies.

@@

1. Our entire workflow is scripted, using the R computing environment `r citep(citation("base"))`. The database can be rebuilt in an instant from the raw datafiles, using a single command. When a single data contribution has been modified, the final master dataset is thus easily recreated.
2. We wrote a new `R` package [dataMashR](https://github.com/dfalster/dataMashR) `r citet("https://github.com/dfalster/dataMashR")` for merging data from different studies in a transparent and reproducible fashion. While it was written with BAAD in mind, the package is designed to be easily  deployed for other compilations.
3. We used version control and the code sharing website [github](www.github.com) to track the evolution of the database and the code to process the raw data. Datasets as well as processing methods inevitably contain errors. With version control, we are able to trace these errors to the source.
4. We used the package `knitr` within `R` to automatically produce reports comparing the raw data provided by a single study to the rest of the database `r citep(citation("knitr"))`. These reports were sent to data contributors for verification, and allowed easy identification of errors in the raw data or processing.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by Daniel Falster and Remko Duursma. Diego Barneche, Rich FitzJohn and Angelica Vårhammar assisted with literature searching, data compilation, and coding. All other authors  contributed data to the project.

>>>>

We (D. Falster and R. Duursma, with the help of D. Barneche, R. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$dataset))` different published and unpublished studies.

@@

1. Our entire work flow is scripted, using the R computing environment `r citep(citation("base"))`. The database can be rebuilt in an instant from the raw datafiles, using a single command. When a single data contribution has been modified, the final master dataset is thus easily recreated.
2. We wrote a new `R` package [dataMashR](https://github.com/dfalster/dataMashR) `r citet("https://github.com/dfalster/dataMashR")` for merging data from different studies in a transparent and reproducible fashion. While it was written with BAAD in mind, the package is designed to be easily  deployed for other compilations.
3. We used version control and the code sharing website [github](www.github.com) to track the evolution of the database and the code to process the raw data. Datasets as well as processing methods inevitably contain errors. With version control, we are able to trace these errors to the source.
4. We used the package `knitr` within `R` to automatically produce reports comparing the raw data provided by a single study to the rest of the database `r citep(citation("knitr"))`. These reports were sent to data contributors for verification, and allowed easy identification of errors in the raw data or processing.

@@

### C. DATA SET DESCRIPTORS:
**1. Originators**: The study was initiated by Daniel Falster and Remko Duursma. Diego Barneche, Rich FitzJohn and Angelica Vårhammar assisted with literature searching, data compilation, and coding. A separate compilation focussing on natural forests in Japan, was collected by Masae Ishihara, with assistance from Tsutom Hiura, Hajime Utsugi and Hiroyuki Tanouchi. All other authors contributed data to the project.
